\EVOSUITE at the SBST 2020 Tool Competition

### 2020-03-25 papers/sbst20/main.tex
Attempt to explain 0% coverage and 0% mutation score.

>>>>

%% FESCAR-15 0% coverage 0% mutation score

\subsubsection*{FESCAR-15} According to the \texttt{transcript.csv} file, it
seems that the generated test cases do cover some lines of code but no
branches/conditions.  Looking at the \texttt{logs.log}, \EVOSUITE also reported
0\% coverage, however there are not any issues in any log file.

%% FESCAR-2 0% coverage 0% mutation score

\subsubsection*{FESCAR-2} No clue.  \EVOSUITE does report some coverage at the
end of the \texttt{logs.log} file, but somehow (and according to JaCoCo) the
generated test suite does not cover any branch.

%% FESCAR-37 86.8% coverage 0% mutation score

\subsubsection*{FESCAR-37} The classpath is incomplete as there is a
\texttt{java.lang.ClassNotFoundException: io.netty.channel.Channel}.

%% GUAVA-110 0% coverage 0.6% mutation score

\subsubsection*{GUAVA-110} No clue.

%% FESCAR-7 73.3% coverage 0% mutation score
%% GUAVA-212 77.6% coverage 0% mutation score
%% GUAVA-22 51.8% coverage 0% mutation score
%% PDFBOX-265 51.8% coverage 0% mutation score

\subsubsection*{GUAVA-212, GUAVA-22, PDFBOX-265, PDFBOX-278, PDFBOX-285,
PDFBOX-40, PDFBOX-91} The mutation analysis failed due to a
\texttt{java.util.concurrent.ExecutionException} thrown by the experimental
infrastructure.

%% PDFBOX-62 1.2% coverage 0% mutation score

\subsubsection*{PDFBOX-62} \EVOSUITE crashed due to some Mocking stuff.

%% SPOON

\subsubsection*{SPOON} There is no \texttt{logs.log} file to check \EVOSUITE's
log messages.  There is any test suite for any SPOON
class.  The reason might be due to
\texttt{java.io.IOException: Not a valid directory name: /var/benchmarks/projects/spoon-core-7.2.0/src/main/java}.
in the \texttt{log\_detailed.txt} file.  Also, all \texttt{transcript.csv} are
empty.  Thus, it seems the experimental infrastructure do not even attempt to
generate test cases for any SPOON class.  Question: how did \EVOSUITE achieved
a 72.5\% coverage for, e.g., SPOON-253 if there is no test suite or even a valid
attempt?
